---
title: "R Programming Task 2"
output: html_notebook
---
1. Object x <-1:15
```{r}
s <- 1:15
dim(s) <- c(4, 1)
print(s)
```
2. Write a program to generate the following 4x4 matrix
```
0 0 0 0
0 0 0 0
0 0 0 0
```
```{r}
a = matrix(rep(0, 9), nrow=4, ncol=4, byrow=TRUE)
print(a)
```

3.The object x<-1:8

```{r}
x <- rbind(1:8, rev(1:8), rep(1, 5))
print(x)
```

4. Chose two different(x,y) 4x4 matrix to perform the following arithmetic operations

```{r}
x <- matrix( c(1, 3, 6, 7, 13, 10, 4, 13, 13, 4, 2, 9, 23, 11, 17, 12), 4, 4, byrow=TRUE )
y <- matrix( c(3, 16, 11, 5, 8, 17, 3, 2, 10, 4, 12, 16, 19, 5, 6, 15), 4, 4, byrow=TRUE )

#Answers are printed in order from a-i
print(x + y)

print(x - y)

print(x * y)

print(x %*% y)

print("(c) is element by element multiplication and (d) is matrix multiplication")

print(solve(y))
z <- x / y

print(z)

print(t(z))

print(diag(t(z)))
```

5. Difference between (i) & (ii)

```{r}
#This is (i)
x <- matrix(x <- 1:9, 3, 3, byrow=TRUE)
print(x)
#This is (ii)
x <- matrix(x <- 1:9, 3, 3)
print(x)

#Answer
print("(i) arranges the matrix row by row and (ii) arranges the matrix column by column.")
```

6. Which function can we use for inner product and outer product in matrix calculation?

```{r}
x <- c(2, 5, 8)
y <- c(7, 4, 1)
print(x %*% y)
print(x %o% y)
#Answer
print("%o% used for outer product, %*% used for inner product")
```

7. Explain the use of all.equal() function in Matrix with a sample program.

```{r}
print("all.equal function is used for comparing attributes, returning NULL or character vector")

#program to explain all.equal() function
m <- matrix( 1:4, ncol=2 )
n <- matrix( 1:4, ncol=2)
print(all.equal(m, n))
print(identical(m, n))
print( m == n )
```

8. Explain the use of dim() function with a sample program.

```{r}
print("dim fucntion is used to return the dimension of the matrix, row and column")

#program to explain dim() function
d <- 2:4
dim(d) <- c(1, 2)
print(d)
```

9. Use of $ operator, and square brackets [] in List with example program.

```{r}
#Program to explain $ operator and square bracket [] in list
list1 <- list(numbers = c(2, 4), logical = TRUE, strings = c("x", "y", "z"))
list1
list1[1]
list1$numbers
sum(list1$numbers)
sum(list1[1])
```

10. Explain ifelse() with example.

```{r}
#Answer
print("ifelse returns a value with the same shape as test which is filled with elements selected from either yes or no depending on whether the element of test is TRUE or FALSE")
x = c(2,5,3,7,4)
ifelse(x %% 2 == 0, "even", "odd")
```

11. Write a program to get the weight and height from the user to calculate the following cases

```{r}
w <- readline(prompt = "Enter the weight: ")
w <- as.integer(w)
w
h <- readline(prompt = "Enter the height: ")
h <- as.integer(h)
h
bmi = round(w / ((h/100)^2), 1)
bmi
ifelse(bmi >= 30.0, "Obesity", 
       ifelse(bmi < 30.0 && bmi >= 25.0, "Overweight", 
              ifelse(bmi < 25.0 && bmi >= 18.5, "Normal", "Underweight")
              )
       )
```

12. Difference between List and Data frame with an example program.

```{r}
#Answer
print("Data frames are lists as well, but they have a few restrictions: you can't use the same name for two different variables. all elements of a data frame are vectors. all elements of a data frame have an equal length")
list1 <- list(15: 25, "R", list(TRUE, FALSE))
list1
```
```{r}
d <- data.frame(face = c("apple", "grape", "pine-apple"),
                 suit = c("red", "purple", "yellow"), value = c(2, 4, 6))
d
```

13. Difference between repeat and while loop with example program.

```{r}
#Answer

print("A repeat loop is used to iterate over a block of code multiple number of times. There is no condition check in repeat loop to exit the loop. We must ourselves put a condition explicitly inside the body of the loop and use the break statement to exit the loop. Failing to do so will result into an infinite loop")
print("while loops are used to loop until a specific condition is met")

x <- 2:10
y <- 3
while(y <= 4) {
  print(x[y])
  y <- y + 1
}

z <- 3
repeat {
  print(x[z])
  z <- z - 1
  if(z <= 1) {
    break
  }
}
```
