---
title: "R Notebook"
output: html_notebook
---

1. Write a R code to Generate 6X6 matrix (A) using the random numbers between 1 to 100 & generate another 6x6 matrix (B) using random numbers between 500 to 600.

```{r}
A<- matrix(1:100, nrow = 6, ncol = 6, byrow = FALSE)
B<- matrix(1:100, nrow= 6, ncol=6, byrow = FALSE)

# a.find the range of matrices A and B
range_A <- range(A)
range_B <- range(B)

# b. find the max value from each row of the matrices A & B

#For matrix A
max.col(A, ties.method = c("random",  "first", "last"))
#for matrix B
max.col(B, ties.method = c("random", "first", "last"))

# c. find the diagonal values of matrices A & B
diag_A <- diag(A)
diag_B <- diag(B)

# d. Multiply A & B
d <- A%*%B
d

# e. replace the 4th row of Matrix A with the diagonal value of B


# f. Multiply matrices A & B and store values on X
x <- A%*%B
x

# g. Divide the matrix A with matrix B
g <- A/B
g
```

2. Create a table using dataframe/tibble with the following categories

```{r}
a <- c("Pong", "Pech", "Pel", "Pich", "Kruy", "Kit", "Sann", "Sim", "Khean", "Hann")
b <- c("Channy", "Sokmeng", "Dane", "Sovannara","Chandara", "Bunrong", "Chamroeun", "Chhay", "Sreythou", "Manich")
c <- c(25, 20, 21, 22, 20, 21, 22, 22, 19, 23)
d <- c("Student","Student","Student","Student","Student","Student","Student","Student","Student","Student")
e <- c("KIT","KIT","KIT","KIT","KIT","KIT","KIT","KIT","KIT","KIT")
f <- 1:10

info <- data.frame(First_name = a, Last_name = b, age = c, Occupation = d, Place = e, Random_number = f)

info

# g. extract the last column
g<- data.frame(info$Random_number)
g

# d. find the sum, mean, and length of the extracted column
sum <- sum(g)
sum
mean <- mean(g)
mean
length <- length(g)
length

```
3. Create a .txt file (min = 150 words) with the lastest news in English in Cambodia from the official news agency's website

```{r}
phnompenhpost <- c("Since the outbreak of Covid-19 early last year, more than 120,000 out of 1.2 million Cambodian migrant workers in Thailand have returned home, with many facing difficulties to sustain themselves and their families.

To ease the burden, the Ministry of Planning has encouraged returning migrants to apply for IDPoor cards with their local authorities. So far, however, only a small portion have applied to join the programme despite widespread hardships.

Phorn Chantha is a 51-year-old farmer from Kors Kralor district’s Chhnal Mann commune in Battambang province. Before the outbreak, he had worked with family members as gardeners for a real estate company in Thailand’s Pathum Thani province for four years.")

write(phnompenhpost, "D:\\R_Programming\\phnompenhpost.txt", append=FALSE)

# a. read the .txt file
read_file <- read.delim("phnompenhpost.txt")

# b. perform the Tokenization and count the words
table_mining <- data.frame(SNo = 1, Text = phnompenhpost)
table_mining %>% 
  unnest_tokens(info, Text) %>%  #list word one by one
  countword <- count(info) %>% #count the words

# c. find the most repeated word and replace with the word "KIT"


# d. Perform Sentiment Analysis
sentiment(table_mining$Text)
sentiment_by(table_mining$Text)
get_sentences(table_mining$Text)
#get the emotion count
emotion_by(table_mining$Text)

# e. Plot the graph
ggplot(data, aes(x= info, y=countword)) +
  geom_col() +
  xlab("Number of Words") +
  ylab("List of words") +
  ggtitle("Text Mining Using R") + 
  
  theme(plot.title=element_text(size=25, color='yellow', face='bold', hjust=0.5, margin=margin(r=25)))
      axis.title.x=element_text(size=10, color='blue', face='bold', margin=margin(r=20),
      axis.title.y=element_text(size=10, color='red', face='bold', margin=margin(r=20)),
     ) 
```

4. Find the assigned Dataset from the list below and perform the following

```{r}
# a. import and clean the dataset

```




